### 2020-11-17 thesis/chap_1.tex
update for last comments
fix space
fixing last of andy's comments

To get a better sense of land use patterns in the region, we ran some preliminary analysis on land use change data at the municipality level. These results are not presented in the main text but are to be found in Appendix 3. 
Montérégie is made up of 177 different municipalities. We generated land use matrices (amount of each land use category) and land cover transition matrices for the first timestep of our dataset (1990 to 2000) for each municipality and for the land use categories corresponding to our model. We then performed multivariate analyses by running a first ordination using PCA (Principal Component Analysis), and then using Ward clustering \citep{legendre_ordination_2012}. The results of this analysis
Because municipalities in Montérégie have variable size, the amount of change in each municipality needed to be standardized. The data was normalized prior to the ordination to reflect relative amounts of change in each municipality. We used the \verb|vegan| package in R to produce such plots.\\

@@

All steps are illustrated on the top right part of figure \ref{fig:workflow1} ("Statistical Modelling").

@@

\begin{figure}[h]
\makebox[\textwidth]{
\includegraphics[width=1.25\textwidth]{thesis/figures/Chapter1_flowchart.png}
}
\caption[Workflow diagram for Chapter 1 (part 1)]{Workflow diagram for Chapter 1 (part 1). This figure shows the methodological steps for data preparation, statistical modelling and land use change modelling. Data layers (parallelograms) were extracted from multiple databases (cylinders) and processed (hexagons) in order to produced the outputs (data tables and raster layers) used for statistical and land use change modelling. The resulting data table was split in test and train sets before runnig the random forest model. Note the multiple outputs of the land use change model which produced different simulations based on scenarios. }
\label{fig:workflow1}
\end{figure}
\clearpage

>>>>

To get a better sense of land use patterns in the region, we ran a preliminary analysis on land use change data at the municipality level. These results are not presented in the main text but are to be found in Appendix 3. 
Montérégie is made up of 177 different municipalities. We generated land use matrices (amount of each land use category) and land cover transition matrices for the first timestep of our dataset (1990 to 2000) for each municipality and for the land use categories corresponding to our model. We then performed multivariate analyses by running a first ordination using PCA (Principal Component Analysis), and then using Ward clustering \citep{legendre_ordination_2012}. The results of this analysis
Because municipalities in Montérégie have variable size, the amount of change in each municipality needed to be standardized. The data was normalized prior to the ordination to reflect relative amounts of change in each municipality. We used the \verb|vegan| package in R to produce such plots.\\

@@

All steps are illustrated on the top right part of figure \ref{fig:workflow1} ("Statistical Modelling"). \\

@@

\begin{figure}[h]
\makebox[\textwidth]{
\includegraphics[width=1.20\textwidth]{thesis/figures/Chapter1_flowchart.png}
}
\caption[Workflow diagram for Chapter 1 (part 1)]{Workflow diagram for Chapter 1 (part 1). This figure shows the methodological steps for data preparation, statistical modelling and land use change modelling. Data layers (parallelograms) were extracted from multiple databases (cylinders) and processed (hexagons) in order to produced the outputs (data tables and raster layers) used for statistical and land use change modelling. The resulting data table was split into test and training datasets before running the random forest model. Note the multiple outputs of the land use change model which produced different simulations based on scenarios. }
\label{fig:workflow1}
\end{figure}
\clearpage

### 2020-11-17 thesis/chap_2.tex
fixing last of andy's comments

The workshop aimed to gather stakeholders from multiple groups:
\begin{enumerate}
  \item Representatives of Non-Governmental Organizations that are involved in the conservation of ecological connectivity within the study extent (i.e. Montérégie).
  \item Land use planners (“amenagistes”) of the administrative regions covered by the study extent (the 15 MRCs in Montérégie).
  \item Representatives of Ministries involved in conservation (MFFP, MELCC).
  \item Representatives of the UPA (“Union des producteurs agricoles”) in Montérégie.
  \item Representatives of the private forestry industry unions (“producteurs forestiers”)
\end{enumerate}
Although representants of this last group was invited to the activity, none attended the workshop. \\

>>>>

The workshop aimed to gather stakeholders from multiple groups:
\begin{enumerate}
  \item Representatives of Non-Governmental Organizations that are involved in the conservation of ecological connectivity within the study extent (i.e. Montérégie).
  \item Land use planners (“amenagistes”) of the administrative regions covered by the study extent (the 15 MRCs in Montérégie).
  \item Representatives of Ministries involved in conservation (MFFP, MELCC).
  \item Representatives of the UPA (“Union des producteurs agricoles”) in Montérégie.
  \item Representatives of the forestry producers union (“producteurs forestiers”)
\end{enumerate}
Although representatives of this last group were invited to the activity, none attended the workshop. \\

### 2020-11-17 thesis/thesis.tex
fixing last of andy's comments

A wide range of socio-ecological methods have been used in general conservation planning (these are reviewed in more details in chapter 2), including participatory mapping. Participatory mapping involves leveraging the knowledge that stakeholders hold about the geography of their landscape, in order to achieve a community-driven objective  \citep{plieninger_assessing_2013}. Scenarios are a flexible approach to forecasting the range of possible futures in landscapes \citep{peterson_scenario_2003}.\\ \vspace{2em}

>>>>

A wide range of socio-ecological methods have been used in general conservation planning (these are reviewed in more detail in chapter 2), including participatory mapping. Participatory mapping involves leveraging the knowledge that stakeholders hold about the geography of their landscape, in order to achieve a community-driven objective  \citep{plieninger_assessing_2013}. Scenarios are a flexible approach to forecasting the range of possible futures in landscapes \citep{peterson_scenario_2003}.\\ \vspace{2em}
